SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source-Term Evaluation

### 2018-05-21 paper.tex
move to derivations

The derivative of the temperature source-term with respect to itself is:
\loadeq{dTdotdT}
with respect to the thermodynamic state-parameter source-term (the volume \slash pressure for \conp/\slash\conv/, respectively) it's derivative:
\loadeq{dTdotdE}
The derivative for the moles of species $j$:
\loadeq{dTdotdnj}

The derivative of the thermodynamic state parameter with respect to the temperature is:
\loadeq{dEdotdT}
and with respect to itself:
\loadeq{dEdotdE}
where $[C]$ is the total molar concentration:
\begin{equation}
 [C] = \frac{P}{\mathcal{R} T}\;.
\end{equation}
Finally, the derivative with respect to the moles of species $j$:
\loadeq{dEdotdnj}

The molar source-terms are more complicated due to the derivatives of the net rate of progress---see~\cref{deriv-s:dropi}---and pressure modification terms---\cref{deriv-s:dci}---of the reactions.
The reader is again encouraged to read the supplemental material covering the exact derivations and equations solved by \texttt{pyJac}.
The derivative of the molar source-term with respect to temperature is:
\loadeq{dnkdotdT}
while, similarly the derivative with respect to the state parameter is:
\loadeq{dnkdotdE}
and the moles of species $j$:
\loadeq{dnkdotdnj}

>>>>

\delete{The derivative of the temperature source-term with respect to itself is:\ldots}
\add{The complete derivation of the Jacobian for \texttt{pyJac} is attached as supplemental material for the interested reader.}
